On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-29 Manuscript/manuscript.tex
removed addressed comments

\usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

\jy{I'd slightly increase the heights of the figures such that two of them
  would occupied a whole page. This reduces the complexity of floating in
  finding best locations.}
\mc{addressed}

\jy{Clarify normal margins in captions.}
\mc{addressed}

@@

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient of $W_t$.
Let $\rho$ be the lag-1 autocorrelation coefficient of $X_t$.
Although we may have set $\rho$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five true autocorrelation coefficients for $W_t$ were different.
\mc{I may need some help explaining the calibration of copula parameters}
\jy{see demo code in \texttt{copula.R}}

To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula with 
$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \textsl{copula} package.
\citep{hofert2018elements} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\phi = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\phi$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}.

\jy{cite the copula book instead of the package} \mc{i cited the nelsen book 
referenced in the manual}
\jy{Cite my book on the copula package}
\mc{addressed}

\jy{Let's call this process marginally transformed AR(1) proess. Itself is not
  an AR(1) process. Correct the captions.}
\mc{addressed}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/exp_pho_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$ 
    transformed to an exponential distribution iwth $\lambda = 1$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:eri}
\end{figure}

>>>>

\usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{orange}{MC: (#1)}}

@@

@@

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient of $W_t$.
Let $\rho$ be the lag-1 autocorrelation coefficient of $X_t$.
Although we may have set $\rho$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five true autocorrelation coefficients for $W_t$ were different.

To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula with 
$\rho \in \{-0.4, -0.2, 0.0, 0.2, 0.4\} $using the \texttt{copula} package.
\citep{hofert2018ealements} Then we computed $E[XY]$, which 
requires double integration using the \texttt{pracma} package. \citep{pracma} 
Finally, we obtained true $\phi = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\phi$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/exp_pho_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for 
    samples of $n \in \{800, 1600\}$ for an AR(1) process with $\phi = 0.4$
    \jy{not accurate}
    transformed to an exponential distribution iwth $\lambda = 1$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:eri}
\end{figure}
